### 2019-10-28 README.Rmd
Update README.Rmd
Removing the spaces in " >= " results in proper in-line display of the R code under "Using `vis_expect()`". It appears that markdown parses the character combination " >" as a line break even when surrounded by back ticks. (Could be manually fixed in README.md by removing line break)

`vis_expect` visualises certain conditions or values in your data. For example,
If you are not sure whether to expect values greater than 25 in your data
(airquality), you could write: `vis_expect(airquality, ~.x >= 25)`, and you can
see if there are times where the  values in your data are greater than or equal
to 25:

>>>>

`vis_expect` visualises certain conditions or values in your data. For example,
If you are not sure whether to expect values greater than 25 in your data
(airquality), you could write: `vis_expect(airquality, ~.x>=25)`, and you can
see if there are times where the  values in your data are greater than or equal
to 25:
